---
title: "simplePlates"
output: github_document
---

A set of simple functions for working with plate-based data.
```{r echo = FALSE}
library(simplePlates)
```
>"omg this is the best thing ever i love simplePlates" - Somayra, 2020

### Installation
```{r eval=FALSE}
devtools::install_github("bradyajohnston/simpleplates")
```

## Example use cases.

### `make_plate()`

For quickly generating sample and concentration data for a plate, to later 
match with observed data. The rows can be either letters or a numeric verctor (_numbers must be > 0 and < 26_).
```{r}
make_plate(
  rows = LETTERS[1:3], 
  cols = 1:3, 
  sample = "foo"
)

make_plate(
  rows = 1:3, 
  cols = 1:3, 
  sample = "foo"
)

make_plate(
  rows = 1:3, 
  cols = 1:3, 
  sample = c("sampleA", "sampleB", "sampleC")
)

make_plate(
  rows = 1:3, 
  cols = 1:3, 
  sample = rep(c("sampleA", "sampleB", "sampleC"), each = 3)
)
```

`make_plate()` can also take concentration information, as well as perform dilution series`.

```{r}
make_plate(
  rows = 1:3, 
  cols = 1:3, 
  sample = c("sampleA", "sampleB", "sampleC"), 
  conc = 500, 
  dil = 0.5, 
  direction = "vertical"
)

make_plate(
  rows = 1:3, 
  cols = 1:3, 
  sample = rep(c("sampleA", "sampleB", "sampleC"), each = 3),
  conc = 500, 
  dil = 0.5, 
  direction = "horizontal"
)

```

<!-- ### `plate_map()` -->

<!-- Cretes a visual representation of a plate's contents. -->
<!-- ```{r} -->
<!-- df1 <- make_plate( -->
<!--   rows = 1:8,  -->
<!--   cols = 1:12,  -->
<!--   sample = rep(c("sampleA", "sampleB", "sampleC"), each = 4), -->
<!--   conc = 500,  -->
<!--   dil = 0.5,  -->
<!--   direction = "vertical" -->
<!-- ) -->

<!-- library(ggplot2) -->

<!-- letter_numbers <- match(unique(df1$rows), LETTERS) -->
<!-- df1$letter_numbers <- match(df1$rows, LETTERS) -->

<!-- ggplot(df1, aes( -->
<!--   x = cols,  -->
<!--   y = letter_numbers, -->
<!--   # shape = sample, -->
<!--   fill = sample -->
<!-- )) +  -->
<!--   geom_raster(aes( -->
<!--     xmin = min(cols), -->
<!--     xmax = max(cols), -->
<!--     ymin = min(letter_numbers), -->
<!--     ymax = max(letter_numbers) -->
<!--   ), alpha = 0.8) + -->
<!--   geom_point(size = 8) + -->
<!--   geom_line(aes( -->
<!--     y = letter_numbers, -->
<!--     x = cols, -->
<!--     group = rows -->
<!--   ), alpha = 0.5) +  -->
<!--   geom_line(aes( -->
<!--     y = letter_numbers,  -->
<!--     x = cols,  -->
<!--     group = cols -->
<!--   ), alpha = 0.5) + -->
<!--   scale_x_continuous(breaks = 1:12, position = "top") + -->
<!--   scale_alpha(position = "bottom") + -->
<!--   scale_y_reverse(breaks = letter_numbers, labels = LETTERS[letter_numbers]) + -->
<!--   theme_linedraw(base_size = 15) + -->
<!--   theme(panel.grid = element_blank(),  -->
<!--         axis.title = element_blank(),  -->
<!--         aspect.ratio = 8/12) + -->
<!--   labs(alpha = "") + -->
<!--   scale_colour_viridis_c(option = "B")  -->
<!-- ``` -->

