---
title: "simplePlates"
output: github_document
---

A set of simple functions for working with plate-based data.
```{r echo = FALSE}
library(simplePlates)
```
>"omg this is the best thing ever i love simplePlates" - Somayra, 2020

### Installation
```{r eval=FALSE}
devtools::install_github("bradyajohnston/simpleplates")
```

## Example use cases.

### `make_plate()`

For quickly generating sample and concentration data for a plate, to later 
match with observed data. The rows can be either letters or a numeric verctor (_numbers must be > 0 and < 26_).
```{r}
make_plate(
  rows = LETTERS[1:3], 
  cols = 1:3, 
  sample = "foo"
)

make_plate(
  rows = 1:3, 
  cols = 1:3, 
  sample = "foo"
)

make_plate(
  rows = 1:3, 
  cols = 1:3, 
  sample = c("sampleA", "sampleB", "sampleC")
)

make_plate(
  rows = 1:3, 
  cols = 1:3, 
  sample = rep(c("sampleA", "sampleB", "sampleC"), each = 3)
)
```

`make_plate()` can also take concentration information, as well as perform dilution series`.

```{r}
make_plate(
  rows = 1:3, 
  cols = 1:3, 
  sample = c("sampleA", "sampleB", "sampleC"), 
  conc = 500, 
  dil = 0.5, 
  direction = "vertical"
)

make_plate(
  rows = 1:3, 
  cols = 1:3, 
  sample = rep(c("sampleA", "sampleB", "sampleC"), each = 3),
  conc = 500, 
  dil = 0.5, 
  direction = "horizontal"
)

```

### `plate_map()`

Cretes a visual representation of a plate's contents.
```{r}
df1 <- make_plate(
  rows = 1:8,
  cols = 1:12,
  sample = rep(c("sampleA", "sampleB", "sampleC"), each = 4),
  conc = 500,
  dil = 0.5,
  direction = "vertical"
)

library(ggplot2)

ggplot(df1, aes(
  x = cols,
  y = match(rows, LETTERS),
  colour = sample
)) +
  geom_point(size = 8) +
  scale_x_continuous(breaks = 1:12, 
                     position = "top", 
                     expand = c(0.05,0.05)) +
  scale_y_reverse(breaks = 1:12, 
                  labels = LETTERS[1:12],
                  expand = c(0.05,0.05)) +
  theme_linedraw(base_size = 15) +
  theme(panel.grid = element_blank(),
        axis.title = element_blank(),
        aspect.ratio = 8/12, 
        legend.position = "bottom") + 
  labs(colour = "Sample")
```

